\vspace{-1.5em} \bf A general and efficient representation of ancestral recombination graphs

### 2024-04-18 paper.tex
Fix figure ref
Closes #443

In eukaryotes, ARGs are a result of the cellular processes of mitosis and meiosis.
Mitosis leads to common ancestor events,
and meiosis leads to recombination events (both crossover and gene conversion).
Fig.~\ref{fig-cell-lines} shows a schematic of the events  and
the genomes (chromosome icons) that occur in the cellular
germline of a simplified, diploid multicellular
hermaphrodite eukaryote with partially overlapping generations.
Here, an event is not represented by a specific
genome. Rather, genomes can be associated with, or ``tag'', events above
(ancestral to) or below (descended from) them.
For example, tagging the two genomes above a recombination event leads to the
two node representation seen in
Fig.~\ref{fig-simplification}A and Fig.~\ref{hudson_vs_bigARG},
whereas tagging the genome
below a recombination event leads to the more
conventional graphs in Figs.~\ref{fig-ancestry-resolution} and \ref{fig-inferred-args}A,B.

>>>>

In eukaryotes, ARGs are a result of the cellular processes of mitosis and meiosis.
Mitosis leads to common ancestor events,
and meiosis leads to recombination events (both crossover and gene conversion).
Fig.~\ref{fig-cell-lines} shows a schematic of the events  and
the genomes (chromosome icons) that occur in the cellular
germline of a simplified, diploid multicellular
hermaphrodite eukaryote with partially overlapping generations.
Here, an event is not represented by a specific
genome. Rather, genomes can be associated with, or ``tag'', events above
(ancestral to) or below (descended from) them.
For example, tagging the two genomes above a recombination event leads to the
two node representation seen in
Fig.~\ref{fig-arg-in-pedigree}A and Fig.~\ref{hudson_vs_bigARG},
whereas tagging the genome
below a recombination event leads to the more
conventional graphs in Figs.~\ref{fig-ancestry-resolution} and \ref{fig-inferred-args}A,B.
